Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
one the way to describe S(C) relates to D

\newcommand{\kOOmt}[0]{\mathtt{stop}}
\newcommand{\kOOconsI}[3]{[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]#3}
\newcommand{\kOOconsII}[2]{[\mathtt{cons} \; #1 \; \square]#2}
\newcommand{\kOOinl}[1]{[\mathtt{inl} \; \square]#1}
\newcommand{\kOOinr}[1]{[\mathtt{inr} \; \square]#1}
\newcommand{\kOOappI}[3]{
	[\square \; \langle#1,#2\rangle ]#3
}
\newcommand{\kOOappII}[2]{
	[#1 \; \square]#2}
\newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
\newcommand{\kOOcdr}[1]{[\mathtt{snd} \; \square]#1}
\newcommand{\kOOcaseI}[4]{
	[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseII}[4]{
	[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseIII}[3]{
	[\mathtt{case} \; #1 \; #2 \; \square]#3}
\newcommand{\kOOcast}[2]{
	[\square \langle #1 \rangle]#2}

@@

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\langle#2\rangle\;#3\langle#4\rangle}
%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\langle#2\rangle}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\langle#2\rangle}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
\newcommand{\continue}[2]{continue(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

	Evaluation \fbox{$\judgeCeval{e}{o}$}
	\[
	\inference{
		\sOOinspect{e}{\emptyset}{cont(\hckOOmt)} \longrightarrow_{B}^{*} 
		\sOOhalt{o}
	}{
		\judgeCeval{e}{o}
	}
	\]

@@

\todo[inline]{We might need to values before Lazy D Cast ADT.}

@@

	Build continuation \fbox{$cont(k) = \kappa$}
	\[
	\begin{array}{rclc}
	\funrule{cont(k)}{\kOOcast{id(T_1)}{k}}{
		\sidecond{k : T_1 \Longrightarrow T_2}}
	\end{array}
	\]

@@

	Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
	\[
	\begin{array}{rclr}
	\hiredruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\hcvOOtt}{\kappa}
	}{}
	\hiredruleS{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{E}{}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{cont(\kOOinl{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{cont(\kOOinr{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\kOOappI{E}{e_2}{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{cont(\kOOcar{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{cont(\kOOcdr{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
		\sOOinspect{e_1}{\rho}{cont(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{}
	\hiredruleS{
		\sOOreturn{v}{\kOOcast{c}{k}}
	}{
	\begin{cases}
	continue(k,v') & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
	\end{cases}
	}{}
%\redruleS{
%	\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
%	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}
%
%\redrule{
%\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
%\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{
%\\&&
%\sidecond{v_1 : T_1 \wedge v_2 : T_2}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinl{\kappa})}}{
%\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinr{\kappa})}}{
%\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
%\sOOinspect{e_2}{\rho}{cont(\kOOappII{v_1}{\kappa})}}{}
%
%	
%	& \vdots \\
%	\redruleS{
%		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
%	}{
%		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
%	}{}
%	\redruleS{
%		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
%	}{
%		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
%	}{}
%	\redruleS{
%		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
%	}{
%		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
%	}{}
%	\redruleS{
%		
%\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
%	}{
%		\begin{cases}
%		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
%		\\
%		\sOOhalt{(\oOOblame{l})} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
%		\end{cases}
%		
%	}{}
	\end{array}
	\]

@@

\funrule{
	\continue{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
	\sOOinspect{e_2}{\rho}{cont(\kOOconsII{v_1}{\kappa})}}{}

@@

\funrule{
	\continue{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}
}{
	\sOOinspect{e_2}{\rho}{
		cont(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})
	}
}{}

@@

\hifunrule{
	\continue{v_3}{(\mathtt{case_3}\;(\hcvOOinl{v}{c})\;
		(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})
		\;\kappa)}
}{
	\sOOreturn{v}{cont(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
}{}

\hifunrule{
	\continue{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}
	{(\mathtt{case_3}\;(\hcvOOinr{v}{c})\;v_2\;\kappa)}
}{
	\sOOreturn{v}{cont(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
}{}

@@

%	Evaluation \fbox{$\judgeSeval{C}{e}{o}$}
%	\[
%	\inference{
%		\judgeSreduceTrans{C}{
%			\sOOinspect{e}{\emptyset}{cont(\hckOOmt)}
%		}{
%			\sOOhalt{o}
%		}		
%	}{
%		\judgeSeval{C}{e}{o}
%	}
%	\]

@@

Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation. Here we omit rules 
that make the relation a congruence.

@@

	\fbox{$\kappa \approx \kappa$}
	\begin{gather*}
	\inference{
		k \approx \kappa
	}{
		cont(k) \approx \kappa
	}
	\quad
	\inference{
		\kappa_1 \approx \kappa_2
	}{
		ext(cast(T_1,l,T_2),\kappa_1) \approx 
		\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2}
	}
	\end{gather*}

@@

And the relation between continuations is defined in terms of $cont(k)$ and 
$ext(c,k) $: \begin{gather*}
\inference{
	k \approx \kappa
}{
	cont(k) \approx \kappa
}
\quad
\inference{
	\kappa_1 \approx \kappa_2
}{
	ext(cast(T_1,l,T_2),\kappa_1)
	\approx
	\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2} 
}
\end{gather*}

>>>>

\newcommand{\kOOmt}[0]{\mathtt{stop}}
\newcommand{\kOOconsI}[3]{[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]#3}
\newcommand{\kOOconsII}[2]{[\mathtt{cons} \; #1 \; \square]#2}
\newcommand{\kOOinl}[1]{[\mathtt{inl} \; \square]#1}
\newcommand{\kOOinr}[1]{[\mathtt{inr} \; \square]#1}
\newcommand{\kOOappI}[3]{
	[\mathtt{app} \; \square \; \langle#1,#2\rangle ]#3
}
\newcommand{\kOOappII}[2]{
	[\mathtt{app} \; #1 \; \square]#2}
\newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
\newcommand{\kOOcdr}[1]{[\mathtt{snd} \; \square]#1}
\newcommand{\kOOcaseI}[4]{
	[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseII}[4]{
	[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseIII}[3]{
	[\mathtt{case} \; #1 \; #2 \; \square]#3}
\newcommand{\kOOcast}[2]{
	[\square \langle #1 \rangle]#2}

@@

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #2 \; #1 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\langle#2\rangle\;#3\langle#4\rangle}
%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\langle#2\rangle}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\langle#2\rangle}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
\newcommand{\continue}[2]{cont(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

	Evaluation \fbox{$\judgeCeval{e}{o}$}
	\[
	\inference{
		\sOOinspect{e}{\emptyset}{wrap(\hckOOmt)} \longrightarrow_{B}^{*} 
		\sOOhalt{o}
	}{
		\judgeCeval{e}{o}
	}
	\]

@@

\todo[inline]{We might need to values before Lazy D Cast ADT. This will reduce 
the extreme height of Fig.~\ref{fig:machine-cekcc} as well. -KC}

@@

	Build continuation \fbox{$wrap(k) = \kappa$}
	\[
	\begin{array}{rclc}
	\funrule{wrap(k)}{\kOOcast{id(T_1)}{k}}{
		\sidecond{k : T_1 \Longrightarrow T_2}}
	\end{array}
	\]

@@

	Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
	\[
	\begin{array}{rclr}
	\hiredruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\hcvOOtt}{\kappa}
	}{}
	\hiredruleS{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{E}{}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{wrap(\kOOinl{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{wrap(\kOOinr{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{wrap(\kOOappI{E}{e_2}{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{wrap(\kOOcar{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{wrap(\kOOcdr{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
		\sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{}
	\hiredruleS{
		\sOOreturn{v}{\kOOcast{c}{k}}
	}{
	\begin{cases}
	\continue{k}{v'} & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
	\end{cases}
	}{}
%\redruleS{
%	\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
%	\sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}
%
%\redrule{
%\sOOreturn{v_2}{(\kOOconsII{v_1}{\kappa})}}{
%\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{
%\\&&
%\sidecond{v_1 : T_1 \wedge v_2 : T_2}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinl{\kappa})}}{
%\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v}{(\kOOinr{\kappa})}}{
%\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{
%\\&&
%\sidecond{v : T}}
%
%\redrule{
%\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
%\sOOinspect{e_2}{\rho}{wrap(\kOOappII{v_1}{\kappa})}}{}
%
%	
%	& \vdots \\
%	\redruleS{
%		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
%	}{
%		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
%	}{}
%	\redruleS{
%		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
%	}{
%		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
%	}{}
%	\redruleS{
%		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
%	}{
%		\sOOinspect{e_1}{\rho}{wrap(\hckOOconsI{e_2}{\rho}{\kappa})}
%	}{}
%	\redruleS{
%		
%\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
%	}{
%		\begin{cases}
%		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOsucc{v'}} 
%		\\
%		\sOOhalt{(\oOOblame{l})} \\
%		\;\;\;\;\;\;\;\;\;\sidecond{applyCast(v,c_1) = \rOOfail{l}}
%		\end{cases}
%		
%	}{}
	\end{array}
	\]

@@

\funrule{
	\continue{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
	\sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}

@@

\funrule{
	\continue{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}
}{
	\sOOinspect{e_2}{\rho}{
		wrap(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})
	}
}{}

@@

\hifunrule{
	\continue{v_3}{(\mathtt{case_3}\;(\hcvOOinl{v}{c})\;
		(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})
		\;\kappa)}
}{
	\sOOreturn{v}{wrap(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
}{}

\hifunrule{
	\continue{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}
	{(\mathtt{case_3}\;(\hcvOOinr{v}{c})\;v_2\;\kappa)}
}{
	\sOOreturn{v}{wrap(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
}{}

@@

%	Evaluation \fbox{$\judgeSeval{C}{e}{o}$}
%	\[
%	\inference{
%		\judgeSreduceTrans{C}{
%			\sOOinspect{e}{\emptyset}{wrap(\hckOOmt)}
%		}{
%			\sOOhalt{o}
%		}		
%	}{
%		\judgeSeval{C}{e}{o}
%	}
%	\]

@@

Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation. Here we omit rules 
that make the relation a congruence.
%
There are two cases where a continuation in \effCEK{C} relates to a 
continuation in \ineffCEKD. When $k \approx \kappa$, adding an identity cast on 
top of $k$ gives a related continuation. When $\kappa_1 \approx \kappa_2$, 
extending $\kappa_1$ and $\kappa_2$ with the same cast gives related results.
%
As for $v \approx v$, there is one rule for the dynamic type, and two rules for 
each ordinary value constructor.

And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $seq(c,c)$.

@@

	\fbox{$\kappa \approx \kappa$}
	\begin{gather*}
	\inference{
		k \approx \kappa
	}{
		wrap(k) \approx \kappa
	}
	\quad
	\inference{
		\kappa_1 \approx \kappa_2
	}{
		ext(cast(T_1,l,T_2),\kappa_1) \approx 
		\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2}
	}
	\end{gather*}

@@

And the relation between continuations is defined in terms of $wrap(k)$ and 
$ext(c,k) $: \begin{gather*}
\inference{
	k \approx \kappa
}{
	wrap(k) \approx \kappa
}
\quad
\inference{
	\kappa_1 \approx \kappa_2
}{
	ext(cast(T_1,l,T_2),\kappa_1)
	\approx
	\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa_2} 
}
\end{gather*}
